---
title: "P8105 Homework 1"
output: github_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
```

# Problem 1
## Downloading the penguins dataset
```{r, echo = FALSE}
data("penguins", package = "palmerpenguins")

dataset_size = c(nrow(penguins), ncol(penguins))

mean_flipper_length = round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)
```

## Description of the penguins dataset
The penguins dataset contains information about 344 penguins from three species: Adelie, Chinstrap, and Gentoo. Important variables include:

* species: Species of the penguin
* island: Island where the penguin was observed
* bill length (mm): Length of the penguin's bill
* bill depth (mm): Depth of the penguin's bill
* flipper length (mm): Length of the penguin's flipper
* body mass (g): Mass of the penguin in grams

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean_flipper_length` mm.

## Creating a Scatterplot of Flipper Length vs Bill Length
```{r, echo = FALSE, warning = FALSE}
ggplot(data = penguins, 
       aes(x = bill_length_mm, 
           y = flipper_length_mm, 
           color = species)
       ) +
  geom_point() + 
  labs(title = "Scatterplot of Flipper Length vs Bill Length", 
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)")
  ggsave("penguins_plot.pdf")
```

# Problem 2
## Creating a Data Frame
```{r}
hw_1_df = tibble(
  sample_normal = rnorm(10), 
  vec_logical = sample_normal > 0, 
  vec_char = c("My", "name", "is", "Tamara", "and", "this", "is", "my", "Homework", "1."), 
  vec_factor = factor(sample(c("Low", "Medium", "High"), 10, replace = TRUE))
)
```

## Taking the Mean of Each Variable
```{r}
mean(pull(hw_1_df, sample_normal))
mean(pull(hw_1_df, vec_logical))
mean(pull(hw_1_df, vec_char))
mean(pull(hw_1_df, vec_factor))
```


# Discussion
The mean for the random sample is `r sample_normal`. The mean for the logical vector is `r vec_logical`. 

When computing the mean of the character vector, a warning message appears stating `r mean(pull(hw_1_df, vec_char))`. We are not able to find the mean as there are no numerical values in the character vector. When computing the mean of the factor vector, a warning message appears stating `r mean(pull(hw_1_df, vec_factor))`. We are not able to find the mean as there are no numerical values or ways to average between the different factor "levels".

```{r, eval = FALSE}
as.numeric(vec_logical)
as.numeric(vec_char)
as.numeric(vec_factor)
```
